---
title: "Tongfei Li STAC33 A1"
output: html_notebook
---

```{r}
library(tidyverse)
```

1(a)
First, I put the url of the data file into new variable called my_url. 
Since the data values are always separated by the same single character, which 
is a space here, so i use read_delim to read the file.
There are 47 rows and 2 columns, as there should be.
```{r}
my_url <- "http://ritsokiguess.site/STAC32/rainfall.txt"
rainfall <- read_delim(my_url," ")
rainfall
```


1(b)
Here, we want to see the rainfall value changes according to the years, so we 
should put the years in x axis as independent variable, and the rainfall value 
at y axis as response variable. 
Since we need to see the rainfall value changes
as the year changes, we should treat both rainfall and year as quantitative 
variables, 2 quantitative variables leads to a scatter plot.
```{r}
ggplot(rainfall, aes(x = Year, y = Rainfall)) + geom_point()
```


1(c)
From the graph, we see very few points in the grey area, which is the 95% confidence interval of mean of rainfall. 
Although we see a weak upward trend by the regression line, the points seems to be randomly scattered in the plot. 
By looking at R Console, adjusted R_squared value is very small (2.248%), so we consider this regression line do not fit our model.
By looking at the p_value (0.1583), it is much bigger than 0.05.
So I would say there is no linear relationship between rainfall and year, and 
the upward trend is not convincing.

```{r}
ggplot(rainfall, aes(x = Year, y = Rainfall)) + geom_point() + geom_smooth(method="lm")
model1 <- lm(Rainfall ~ Year, data = rainfall)
summary(model1)
```


2(a)
From the data file, we can see that the laptop and score value are separeted by 
more than one space, and the spaces between values are not constant, so I used
read_table here.
There are 47 rows and 2 columns, as there should be. 
I get correct number of observation 47, and correct type of column.
Column 1 is charactor (yes or no) for laptop, which is categorical.
Column 2 is double for score that each student get, which is quantitative.
```{r}
my_url <- "http://ritsokiguess.site/STAC33/algebra.txt"
score <- read_table(my_url)
score
```



2(b)
Since the laptop here is categorical variable and score here is quantitative variable.
1 categorical and 1 quantitative variable leads to side-by-side box plots.
```{r}
ggplot(score, aes(x = laptop, y = score)) + geom_boxplot()
```


2(c)
In the side-by-side box plots we can read:
1. Mean score got by students with laptops (about 84) are higher than students without laptops (about 81).
2. For IQR value (3th quantile - 1th quantile), which is the height of the box, 
IQR for students with laptops is smaller than students without laptops, 
which means the variation of students without laptop is higher, and the students with laptops has more stable score.
3. Students with laptops has higher maximum score (about 100) than students without laptops(about 98).
4. Students with laptops has higher minimum score (about 47) than students without laptops(about 39).
In conclusion, I suggest that students with laptops generally do better and have more stable score than students without laptops.


2(d)
In the box plot, we can see the median score of students with and without laptop is around 84 and 81, which is consistent with what we get from this question.
In the box plot, we can see the 1st and 3rd quartile for students with laptop is around 80 and 93, iqr = 93 - 80 = 13, for students without laptop is aournd 69 and 89, iqr = 89 - 69 = 20, the value we get here is also consistent with box plot.
```{r}
score %>% 
  group_by(laptop) %>%
  summarise(across(where(is_numeric), list(med=~median(.), iqr=~IQR(.))))
```







